### 2024-05-20 index.qmd
20240520 - Patrick Carroll

I thank Benjamin Motz, who provided consultation and many helpful resources based on his fantasy football statistics class.
I also thank key members of [FantasyFootballAnalytics.net](http://fantasyfootballanalytics.net), including Val Pinskiy, Andrew Tungate, Dennis Andersen, and Adam Peterson, who helped develop and provide fantasy football-related resources and who helped sharpen my thinking about the topic.

>>>>

I thank Dr. Benjamin Motz, who provided consultation and many helpful resources based on his fantasy football statistics class.
I also thank key members of [FantasyFootballAnalytics.net](http://fantasyfootballanalytics.net), including Val Pinskiy, Andrew Tungate, Dennis Andersen, and Adam Peterson, who helped develop and provide fantasy football-related resources and who helped sharpen my thinking about the topic.
I also thank Professor Patrick Carroll, who taught me the value of statistics for answering important questions.

### 2024-05-20 intro.qmd
20240520 - Patrick Carroll

Many students find statistics intimidating in part because of how it is typically taught—with examples like dice rolls and coin flips that are not particularly exciting to students.
My contention is that applied examples are a more effective lens to teach many concepts in psychology and data analysis.
It can be more engaging and relatable to learn statistics in the applied context of sports, a domain that is more intuitive to many.
Many people play fantasy sports.
This book involves applying statistics to a particular domain (football).
People actually want to learn statistical principles and methods when they can apply them to interesting questions (e.g., sports).
In my opinion [and supported by evidence; @Motz2013], this is a much more effective way of engaging people and teaching statistics than in the context of abstract coin flips and dice rolls.
Fantasy football relies heavily on prediction—trying to predict which players will perform best and selecting them accordingly.
In this way, fantasy football provides a plethora of decision making opportunities in the face of uncertainty, and a wealth of data for analyzing these decisions.
However, unlike many other applied domains in psychology, fantasy football (1) allows a person to see the accuracy of their predictions on a timely basis and (2) provides a safe environment for friendly competition.
Thus, it provides a unique domain to evaluate—and improve—the accuracy of various prediction models.

>>>>

I was fortunate to have an excellent instructor who taught me the value of learning statistics to answer interesting and important questions.
That is, I do not find statistics intrinsically interesting; rather, I find them interesting because of what they allow me to do.
Many students find statistics intimidating in part because of how it is typically taught—with examples like dice rolls and coin flips that are (seemingly irrelevant and) boring to students.
My contention is that applied examples are a more effective lens to teach many concepts in psychology and data analysis.
It can be more engaging and relatable to learn statistics in the applied context of sports, a domain that is more intuitive to many.
Many people play fantasy sports.
This book involves applying statistics to a particular domain (football).
People actually want to learn statistical principles and methods when they can apply them to interesting questions (e.g., sports).
In my opinion [and supported by evidence; @Motz2013], this is a much more effective way of engaging people and teaching statistics than in the context of abstract coin flips and dice rolls.
Fantasy football relies heavily on prediction—trying to predict which players will perform best and selecting them accordingly.
In this way, fantasy football provides a plethora of decision making opportunities in the face of uncertainty, and a wealth of data for analyzing these decisions.
However, unlike many other applied domains in psychology, fantasy football (1) allows a person to see the accuracy of their predictions on a timely basis and (2) provides a safe environment for friendly competition.
Thus, it provides a unique domain to evaluate—and improve—the accuracy of various prediction models.
